Learning can mediate the evolution of\\ (cheap and costly) signals of quality

### 2020-10-22 Presentations/GenesAsEnviron.tex
New folder to contain presentation and manuscripts. Relevent files moved accordingly. Code needs to be updated to this change. New presentaion started for AGA symposium. New simulations varyinh alphaAct. Need to check why individuals of different quality are not asssorting in nIntGroupEvol4.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Badges of status and Individual Recognition mediated by learning},
  pdfauthor={Andrés Quiñones},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array}

\title{Badges of status and Individual Recognition mediated by learning}
\author{Andrés Quiñones}
\date{September 15, 2020}

@@

\begin{frame}

@@

\begin{center}\includegraphics[width=1\linewidth]{Simulations/alphaAct_/alphaAct0.6learnDyn} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{Simulations/betCostEvol1_/evolDynAll_betCost5} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}

@@

\includegraphics[height=0.28\textheight]{Simulations/betCostEvol1_/evolDistAlpha0_betCost5} \includegraphics[height=0.28\textheight]{Simulations/betCostEvol1_/evolDistBeta0_betCost5} \includegraphics[height=0.28\textheight]{Simulations/betCostEvol1_/evolDistBadge0_betCost5} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\begin{center}\includegraphics[width=1\linewidth]{Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations/betCostEvol1_/BehavIntALL} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations/betCostEvol1_/CueALL} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations/nIntGroupEvol1_/evolDynALL_nIntGroup2000} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Simulations/nIntGroupEvol1_/evolDyn8_nIntGroup2000} \end{center}

@@

\includegraphics[height=0.28\textheight]{Simulations/nIntGroupEvol1_/evolDistAlpha8_nIntGroup2000} \includegraphics[height=0.28\textheight]{Simulations/nIntGroupEvol1_/evolDistBeta8_nIntGroup2000} \includegraphics[height=0.28\textheight]{Simulations/nIntGroupEvol1_/evolDistBadge8_nIntGroup2000} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\begin{flushleft}\includegraphics[width=0.9\linewidth]{Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup2000} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=0.9\linewidth]{Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup2000} \end{flushleft}

@@

\begin{center}\includegraphics[width=1\linewidth]{Images/networks} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations/nIntGroupCost_/BehavIntALL} \includegraphics[width=0.9\linewidth]{Simulations/nIntGroupCost_/CueALL} \end{center}

@@

\begin{center}\includegraphics[width=0.85\linewidth]{Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup10} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup10} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations/nIntGroupCenters1_/evolDynALL_nIntGroup10} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{Simulations/nIntGroupCenters1_/corrAlphBet_nIntGroup10} \end{center}

@@

\begin{flushleft}\includegraphics[height=0.28\textheight]{Simulations/nIntGroupCenters1_/evolDistAlpha5_nIntGroup10} \includegraphics[height=0.28\textheight]{Simulations/nIntGroupCenters1_/evolDistBeta5_nIntGroup10} \includegraphics[height=0.28\textheight]{Simulations/nIntGroupCenters1_/evolDistBadge5_nIntGroup10} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=0.9\linewidth]{Images/cartoonRBF_InitAct} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/evolDynALL_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/evolDyn2_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[height=0.28\textheight]{Simulations/initAct_/evolDistAlpha2_initAct2} \includegraphics[height=0.28\textheight]{Simulations/initAct_/evolDistBeta2_initAct2} \includegraphics[height=0.28\textheight]{Simulations/initAct_/evolDistBadge2_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/corrAlphBet_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/evolDynALL_initAct-2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/evolDyn0_initAct-2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/corrAlphBet_initAct-2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/evolDynALL_initAct-0.69} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/evolDyn0_initAct-0.69} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{Simulations/initAct_/corrAlphBet_initAct-0.69} \end{flushleft}

@@

\begin{center}\includegraphics[height=0.8\textheight]{Images/BizarroParrot} \end{center}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones PhD.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array}

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
October 21, 2020}

@@

\begin{frame}{Social interactions}
\protect\hypertarget{social-interactions}{}

\begin{block}{The need partners with actions}

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \includegraphics[width=0.4\linewidth]{../Images/begging} \includegraphics[width=0.4\linewidth]{../Images/broodparasite} \includegraphics[width=0.4\linewidth]{../Images/dominance} \end{center}

\begin{frame}{The effect of communication}
\protect\hypertarget{the-effect-of-communication}{}

\begin{center}\includegraphics[width=0.8\linewidth]{../Images/harm} \end{center}

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals}{}

\begin{block}{Badge of status}

\begin{center}\includegraphics[height=0.8\textheight]{../Images//hosp_alexandra_mackenzie} \end{center}

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-1}{}

\begin{block}{When are signals honest?}

\begin{itemize}
\tightlist
\item
  Impossible to fake
\item
  Individuals have common interests
\item
  Handicap principle (signal´s cost is proportional to quality)
\end{itemize}

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-2}{}

\begin{block}{Individual recognition}

\begin{center}\includegraphics[height=0.7\textheight]{../Images//indRecog} \end{center}

(Tibbetts and Dale 2007)

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-3}{}

\begin{block}{BS or IR?}

\begin{center}\includegraphics[height=0.75\textheight]{../Images//IRvsBS} \end{center}

(Sheehan and Bergman 2016)

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-4}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Images//comSystemBot} \end{center}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Images//pavlov} \end{center}

\hypertarget{associative-learning}{%
\section{Associative learning}\label{associative-learning}}

\begin{frame}{Reinforcement learning theory}
\protect\hypertarget{reinforcement-learning-theory}{}

\begin{columns}[T]
 \column{0.5\linewidth}
 \begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
  \end{equation*}
  \pause
  \includegraphics[width=1\textwidth]{../Images//learn_curve.png}
 \column{0.5\linewidth}
  \pause
  \includegraphics[height=.9\textheight]{../Images//predErrorNeur.png}
\end{columns}

\begin{frame}{Reinforcement learning theory}
\protect\hypertarget{reinforcement-learning-theory-1}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Images//learnUpdate} \end{center}

\begin{frame}{The Hawk-Dove game}
\protect\hypertarget{the-hawk-dove-game}{}

Individuals have one of two genetically determined phenotypic
strategies. \emph{Hawks} are willing to start a conflict over resources,
while \emph{doves} prefer to stand down in the hope to share the
resource without an aggressive contest.

\begin{center}\includegraphics[width=0.5\linewidth]{../Images//HDgame} \end{center}

\begin{frame}{The hawk-dove game}
\protect\hypertarget{the-hawk-dove-game-1}{}

\begin{align*}
w_H &= p_H \frac{V-C}{2}+(1-p_h) V\\
w_D &= p_H 0 + (1-p_H)\frac{V}{2}
\end{align*} \vspace{-0.8cm}

\begin{center}\includegraphics[width=0.55\linewidth]{../Images//Hawk_dove_plot} \end{center}

\begin{frame}{Environmental states}
\protect\hypertarget{environmental-states}{}

\begin{block}{Discrete states}

\includegraphics[width=0.8\textwidth]{../Images//discreteStates.png}

\begin{block}{Continuos states}

\includegraphics[width=0.8\textwidth]{../Images//contStates.png}

\begin{frame}{Continuos environmental states}
\protect\hypertarget{continuos-environmental-states}{}

\begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
\end{equation*}

\begin{figure}
\includegraphics[width=0.6\linewidth]{../Images/cartoonRBF} \caption{\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.}\label{fig:fig2}
\end{figure}

\hypertarget{our-model}{%
\section{Our model}\label{our-model}}

\begin{frame}{The hawk-dove game 2.0}
\protect\hypertarget{the-hawk-dove-game-2.0}{}

\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{1cm} | >{\centering\arraybackslash}p{4.5cm} | >{\centering\arraybackslash}p{4.5cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

\begin{equation*}
p_w=\frac{1}{1+e^{-\beta(Q_i-Q_j)}}
\end{equation*}

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-11-1} \end{center}

\begin{frame}{Sender Code}
\protect\hypertarget{sender-code}{}

\begin{equation*}
s_i = \frac{1}{1+e^{-(\epsilon_i+\gamma_iQ_i)}}
\label{eq:react_norm}
\end{equation*}

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-12-1} \end{center}

\begin{frame}{Receiver code}
\protect\hypertarget{receiver-code}{}

\begin{equation*}
  \Delta V_{t(s)}=\alpha (R_t-V_t)
\end{equation*}

\begin{center}\includegraphics[width=0.6\linewidth]{../Images/cartoonRBF} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/alphaAct_/alphaAct0.6learnDyn} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/betCostEvol1_/evolDynAll_betCost5} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}

@@

\includegraphics[height=0.28\textheight]{../Simulations/betCostEvol1_/evolDistAlpha0_betCost5} \includegraphics[height=0.28\textheight]{../Simulations/betCostEvol1_/evolDistBeta0_betCost5} \includegraphics[height=0.28\textheight]{../Simulations/betCostEvol1_/evolDistBadge0_betCost5} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-17}
\end{figure}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/betCostEvol1_/BehavIntALL} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/betCostEvol1_/CueALL} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/nIntGroupEvol1_/evolDynALL_nIntGroup2000} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/nIntGroupEvol1_/evolDyn8_nIntGroup2000} \end{center}

@@

\includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol1_/evolDistAlpha8_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol1_/evolDistBeta8_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol1_/evolDistBadge8_nIntGroup2000} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-23}
\end{figure}

@@

\begin{flushleft}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup2000} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup2000} \end{flushleft}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Images/networks} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCost_/BehavIntALL} \includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCost_/CueALL} \end{center}

@@

\begin{center}\includegraphics[width=0.85\linewidth]{../Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup10} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup10} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCenters1_/evolDynALL_nIntGroup10} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCenters1_/corrAlphBet_nIntGroup10} \end{center}

@@

\begin{flushleft}\includegraphics[height=0.28\textheight]{../Simulations/nIntGroupCenters1_/evolDistAlpha5_nIntGroup10} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupCenters1_/evolDistBeta5_nIntGroup10} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupCenters1_/evolDistBadge5_nIntGroup10} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=0.9\linewidth]{../Images/cartoonRBF_InitAct} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDynALL_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDyn2_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[height=0.28\textheight]{../Simulations/initAct_/evolDistAlpha2_initAct2} \includegraphics[height=0.28\textheight]{../Simulations/initAct_/evolDistBeta2_initAct2} \includegraphics[height=0.28\textheight]{../Simulations/initAct_/evolDistBadge2_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/corrAlphBet_initAct2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDynALL_initAct-2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDyn0_initAct-2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/corrAlphBet_initAct-2} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDynALL_initAct-0.69} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDyn0_initAct-0.69} \end{flushleft}

@@

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/corrAlphBet_initAct-0.69} \end{flushleft}

@@

\begin{center}\includegraphics[height=0.8\textheight]{../Images/BizarroParrot} \end{center}

@@

\leavevmode\hypertarget{ref-sheehan_There_2016}{}%
Sheehan, Michael J., and Thore J. Bergman. 2016. ``Is There an
Evolutionary Trade-Off Between Quality Signaling and Social
Recognition?'' \emph{Behav Ecol} 27 (1): 2--13.
\url{https://doi.org/10.1093/beheco/arv109}.

\leavevmode\hypertarget{ref-tibbetts_Individual_2007}{}%
Tibbetts, Elizabeth A., and James Dale. 2007. ``Individual Recognition:
It Is Good to Be Different.'' \emph{Trends in Ecology \& Evolution} 22
(10): 529--37. \url{https://doi.org/10.1016/j.tree.2007.09.001}.
